Local Type Inference for Polarised System F with Existentials

### 2024-05-08 oopsla24/tex/04-algorithm.tex
edit

The singularity of constraint \emph{entries} is defined in
\cref{fig:constraint-entry-singularity}. 
\begin{itemize}
  \item The \emph{equivalence} entries are
    always singular, as the only possible type satisfying them is the one given in
    the constraint itself, which is reflected in rules \ruleref{\ottdruleSINGNEqLabel} and
    \ruleref{\ottdruleSINGPEqLabel}. 
  \item The \emph{subtyping} constraints are trickier.
    As will be discussed in \cref{sec:proof-lub-upgrade}, variables (and equivalent
    them $[[∃nas.pa]]$) do not have proper supertypes, and thus, the
    constraints of a form $[[pua :≥ ∃nas.pa]]$ are singular with the only possible
    normalized solution $[[pa]]$---see rule \ruleref{\ottdruleSINGSupVarLabel}. 
  \item However, if the body of the existential type is guarded by a shift $[[∃nas.↓iN]]$, it is
    singular if and only if $[[iN]]$ is equivalent to some $[[αi⁻ ∊ {nas}]]$ bound
    by the quantifier---see rule \ruleref{\ottdruleSINGSupShiftLabel}.
\end{itemize}

>>>>

The singularity of constraint \emph{entries} is defined in
\cref{fig:constraint-entry-singularity}. 
\begin{itemize}
  \item The \emph{equivalence} entries are
    always singular, as the only possible type satisfying them is the one given in
    the constraint itself, which is reflected in rules \ruleref{\ottdruleSINGNEqLabel} and
    \ruleref{\ottdruleSINGPEqLabel}. 
  \item The \emph{subtyping} constraints are trickier.
    As will be discussed in \cref{sec:proof-lub-upgrade}, variables (and equivalent
    them $[[∃nas.pa]]$) do not have proper supertypes, and thus, the
    constraints of a form $[[pua :≥ ∃nas.pa]]$ are singular with the only possible
    normalized solution $[[pa]]$---see rule \ruleref{\ottdruleSINGSupVarLabel}. 
  \item However, if the body of the existential type is guarded by a shift
    $[[∃nas.↓iN]]$, it is singular if and only if $[[iN]]$ is equivalent to some
    $[[αi⁻ ∊ {nas}]]$ bound by the quantifier---see rule
    \ruleref{\ottdruleSINGSupShiftLabel}. The completeness of this criterion is
    justified by the fact that if $[[iN]]$ is \emph{not} equivalent to any
    $[[αi⁻]]$, then there are two non-equivalent solutions of constraint $[[(pua :≥
    ∃nas.↓iN)]]$: the trivial $[[∃nas.↓iN]]$ and $[[∃nas.↓a1⁻]]$ (which is a
    supertype of $[[∃nas.↓iN]]$ since $[[a1⁻]]$ can be instantiated to
    $[[iN]]$).

\end{itemize}
